---
output: 
  github_document:
    toc: true
    toc_depth: 1
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
<!-- badges: start -->
[![R-CMD-check](https://github.com/ThinkR-open/prenoms/workflows/R-CMD-check/badge.svg)](https://github.com/ThinkR-open/prenoms/actions)
<!-- badges: end -->

# About

`{prenoms}` (namely "firstnames") allows you to explore the data on first names given to children born in metropolitan France between 1900 and 2020.

These data are available at the French level and by department.

Source: These statistics come from the French civil status. They have been collected by the National Institute of Statistics and Economic Studies (Insee), that collects, analyses and disseminates information on the French economy and society. These statistics are available [here](https://www.insee.fr/fr/statistiques/2540004#documentation).

# Installation

You can install the development version of {prenoms} from GitHub:
```
devtools::install_github( "ThinkR-open/prenoms" )
library("prenoms")
```



# Utilisation

For example, names from current [ThinkR](https://thinkr.fr) staff through time: [Colin](https://github.com/colinfay),
[Diane](https://github.com/DianeBeldame),
[Sébastien](https://github.com/statnmap),
[Cervan](https://github.com/Cervangirard),
[Vincent](https://github.com/VincentGuyader),
[Margot](https://github.com/MargotBr)
[Arthur](https://github.com/ArthurData),
[Antoine](https://github.com/ALanguillaume) &
[Florence](https://github.com/FlorenceMounier)

```{r warning=FALSE, message=FALSE}
library("ggplot2")
library("dplyr")
library("tidyr")
library(prenoms)

# In France
load("data/prenoms_france.rda")

   thinkrs <- prenoms_france %>%
     filter(
         name == "Colin"  & sex == "M" |
         name == "Diane"   & sex == "F" |
         name == "Sébastien"  & sex == "M" |
         name == "Cervan"  & sex == "M" |
         name == "Vincent" & sex == "M" |
         name == "Margot"  & sex == "F" |
         name == "Arthur" & sex == "M" |
         name == "Antoine" & sex == "M" |
         name == "Florence"  & sex == "F" 
     ) %>%
     complete(
       name = c("Colin", "Diane", "Sébastien", "Cervan", "Vincent", "Margot", "Arthur", "Antoine", "Florence"),
       year = 1900:2020,
       fill = list(n=0, prop=0)
       ) %>% 
     group_by(name, year, sex) %>%
     summarise(n = sum(n),
               .groups = "drop") %>%
     arrange(year) %>% 
     mutate(
       sex = case_when(
         is.na(sex) & name == "Colin" ~ "M",
         is.na(sex) & name == "Diane" ~ "F",
         is.na(sex) & name == "Sébastien" ~ "M",
         is.na(sex) & name == "Cervan" ~ "M",
         is.na(sex) & name == "Vincent" ~ "M",
         is.na(sex) & name == "Margot" ~ "F",
         is.na(sex) & name == "Arthur" ~ "M",
         is.na(sex) & name == "Antoine" ~ "M",
         is.na(sex) & name == "Florence" ~ "F",
         TRUE ~ sex
       )
     )

   thinkrs %>%
     ggplot() +
     aes(x = year, y = n, color = name) + 
     geom_line() + 
     scale_x_continuous( breaks = seq(1900, 2020, by = 10) ) +
     labs(title = "ThinkR's team names evolution in the 93 department") +
     theme_bw()
```
```{r}
# In the department number of ThinkR's head office: 93

load("data/prenoms.rda")

   thinkrs <- prenoms %>%
     filter(
         name == "Colin"  & sex == "M" |
         name == "Diane"   & sex == "F" |
         name == "Sébastien"  & sex == "M" |
         name == "Cervan"  & sex == "M" |
         name == "Vincent" & sex == "M" |
         name == "Margot"  & sex == "F" |
         name == "Arthur" & sex == "M" |
         name == "Antoine" & sex == "M" |
         name == "Florence"  & sex == "F"
     ) %>%
     filter(dpt == 93) %>%
     complete(
       name = c("Colin", "Diane", "Sébastien", "Cervan", "Vincent", "Margot", "Arthur", "Antoine", "Florence"),
       year = 1900:2020,
       fill = list(n=0, prop=0)
       ) %>% 
     group_by(name, year, sex) %>%
     summarise(n = sum(n),
               .groups = "drop") %>%
     arrange(year) %>% 
     mutate(
       sex = case_when(
         is.na(sex) & name == "Colin" ~ "M",
         is.na(sex) & name == "Diane" ~ "F",
         is.na(sex) & name == "Sébastien" ~ "M",
         is.na(sex) & name == "Cervan" ~ "M",
         is.na(sex) & name == "Vincent" ~ "M",
         is.na(sex) & name == "Margot" ~ "F",
         is.na(sex) & name == "Arthur" ~ "M",
         is.na(sex) & name == "Antoine" ~ "M",
         is.na(sex) & name == "Florence" ~ "F",
         TRUE ~ sex
       )
     )

   thinkrs %>%
     ggplot() +
     aes(x = year, y = n, color = name) + 
     geom_line() + 
     scale_x_continuous( breaks = seq(1900, 2020, by = 10) ) +
     labs(title = "ThinkR's team names evolution in the 93 department") +
     theme_bw()
```

