---
output: 
  github_document:
    toc: true
    toc_depth: 1
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
<!-- badges: start -->
[![R-CMD-check](https://github.com/ThinkR-open/prenoms/workflows/R-CMD-check/badge.svg)](https://github.com/ThinkR-open/prenoms/actions)
<!-- badges: end -->

# About

`{prenoms}` (namely "firstnames") allows you to explore the data on first names given to children born in metropolitan France between 1900 and 2020.

These data are available at the French level and by department.

> Source: These statistics come from the French civil status. They have been collected by the National
Institute of Statistics and Economic Studies (Insee), that collects, analyses and disseminates
information on the French economy and society. These statistics are available
[here](https://www.insee.fr/fr/statistiques/2540004#documentation).

# Installation

You can install the development version of {prenoms} from GitHub:

```{r, eval= FALSE}
devtools::install_github( "ThinkR-open/prenoms" )
library("prenoms")
```

# Usage

```{r warning=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
library(purrr)
library(prenoms)
```

For example, names from current [ThinkR](https://thinkr.fr) staff through time:

* [Colin](https://github.com/colinfay)
* [Diane](https://github.com/DianeBeldame)
* [Sébastien](https://github.com/statnmap)
* [Cervan](https://github.com/Cervangirard)
* [Vincent](https://github.com/VincentGuyader)
* [Margot](https://github.com/MargotBr)
* Estelle
* [Arthur](https://github.com/ArthurData)
* [Antoine](https://github.com/ALanguillaume)
* [Florence](https://github.com/FlorenceMounier)
* [Murielle](https://github.com/MurielleDelmotte)

Let's define a dataset holding our names and genders:

```{r}
team_members <- tribble(
  ~name,      ~sex, 
  "Colin",     "M", 
  "Diane",     "F", 
  "Sébastien", "M", 
  "Cervan",    "M", 
  "Vincent",   "M", 
  "Margot",    "F",
  "Estelle",  " F",
  "Arthur",    "M", 
  "Antoine",   "M", 
  "Florence",  "F",
  "Murielle",  "F"
)
```

And then craft a function that will retrieve only the names corresponding to our own names.

```{r}
get_thinkr_team_name_data <- function(
  prenoms_df, 
  team_members_df
) {
  prenoms_df %>% 
    # Get data corresponding only to team member names
    inner_join(
      team_members, 
      by = c("name", "sex")
    ) %>%
    # Add missing combination for name x year 
    complete(
      name = team_members$name,
      year = 1900:2020,
      fill = list( n = 0, prop = 0 )
    ) %>% 
    group_by(name, year, sex) %>%
    summarise(
      n = sum(n),
      .groups = "drop"
    ) %>%
    arrange(year) %>% 
    # If sex is not define (NA) we assumed it was
    # the same as the corresponding team member's
    mutate(
      sex = map2_chr(
        sex,
        name,
        function(
          sex,
          name
        ) {
          ifelse(
            is.na(sex) & name %in% team_members$name,
            team_members$sex[team_members$name == name],
            sex
          )
        }
      )
    )
}
```

### At France country scale

```{r}
# Data for the whole France
data(prenoms_france)

thinkrs <- get_thinkr_team_name_data(
  prenoms_df = prenoms_france,
  team_members_df = team_members
)
```

```{r, graph-france, fig.dim=c(7,5)}
thinkrs %>%
  ggplot() +
  aes(x = year, y = n, color = name) +
  geom_line() +
  scale_x_continuous( breaks = seq(1900, 2020, by = 10) ) +
  labs(title = "ThinkR's team names evolution in France") +
  theme_bw()
```

### In the "départment" of ThinkR's headquarters: 93 (Seine-Saint-Denis)

```{r}
# Data by "départment"
data(prenoms)

thinkrs_93 <- prenoms %>%   
  filter(dpt == 93) %>%
  get_thinkr_team_name_data(
    team_members
  )
```

```{r, graph-departement, fig.dim=c(7,5)}
thinkrs_93 %>%
  ggplot() +
  aes(x = year, y = n, color = name) +
  geom_line() +
  scale_x_continuous( breaks = seq(1900, 2020, by = 10) ) +
  labs(title = "ThinkR's team names evolution in the 93 department") +
  theme_bw()
```

